---
title: "sparseGraph"
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
library(knitr)
opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center",
  fig.retina = 2,
  out.width = "75%",
  dpi = 96
)
knit_hooks$set(pngquant = hook_pngquant)
```

# fingraph

ADMM-like algorithms for learning graphs from data with applications to financial markets.

## Installation

You can install the development version from GitHub:
```{r, eval = FALSE}
> devtools::install_github("mirca/fingraph")
```

#### Microsoft Windows
On MS Windows environments, make sure to install the most recent version of ``Rtools``.

## Usage

## Citation
If you made use of this software please consider citing:

-   [J. V. de M. Cardoso](https://mirca.github.io), [J. Ying](https://github.com/jxying),
    [D. P. Palomar](https://www.danielppalomar.com) (2021).
    [Graphical Models in Heavy-Tailed Markets](https://palomar.home.ece.ust.hk/papers/2021/CardosoYingPalomar-NeurIPS2021.pdf).
    [Advances in Neural Information Processing Systems](https://neurips.cc/Conferences/2021) (NeurIPS’21).

## Links
- [NeurIPS’21 Slides](https://palomar.home.ece.ust.hk/papers/2021/CardosoYingPalomar-NeurIPS2021-slides.pdf)
- [NeurIPS'21 Poster](https://palomar.home.ece.ust.hk/papers/2021/CardosoYingPalomar-NeurIPS2021-poster.png)
- [NeurIPS'21 Supplementary Material](https://palomar.home.ece.ust.hk/papers/2021/CardosoYingPalomar-NeurIPS2021-supplemental.pdf)
